Comparing some optimization methods to obtain estimations in the Gompertz-lognormal diffusion process

### 2015-01-22 paper.tex
Cambia de directorio los ficheros, pero falta uno @nuriastatgirl

\begin{figure}
  \centering
\begin{tabular}{ c c }
  \epsfig{file=./Graficas/graf1prueba.eps,width=.50\textwidth} & \epsfig{file=./Graficas/graf2prueba.eps,width=.50\textwidth} \\
  $\sigma^2=10^{-5}$ & $\sigma^2=10^{-4}$ \\
  \epsfig{file=./Graficas/graf3prueba.eps,width=.50\textwidth} & \epsfig{file=./Graficas/graf4prueba.eps,width=.50\textwidth} \\
  $\sigma^2=10^{-3}$ & $\sigma^2=10^{-2}$\\
\end{tabular}
\caption{\footnotesize{Simulated paths for Gompertz-lognormal process from $t_0=1$ to $t_{500}=100$, with values $m=1$, $\beta=0.2$, and $c=0.013$ and different values of noise; $\sigma^2=10^{-5}$, $\sigma^2=10^{-4}$, $\sigma^2=10^{-3}$ and  $\sigma^2=10^{-2}$. Black lines highlight the paths last value $x_{i;500}$ are maximum, minimum and the quartiles of the output range. }} \label{1:figura:path}
\end{figure}

>>>>

\begin{figure}
  \centering
\begin{tabular}{ c c }
  \epsfig{file=graf1prueba.eps,width=.50\textwidth} & \epsfig{file=graf2prueba.eps,width=.50\textwidth} \\
  $\sigma^2=10^{-5}$ & $\sigma^2=10^{-4}$ \\
  \epsfig{file=graf3prueba.eps,width=.50\textwidth} & \epsfig{file=graf4prueba.eps,width=.50\textwidth} \\
  $\sigma^2=10^{-3}$ & $\sigma^2=10^{-2}$\\
\end{tabular}
\caption{\footnotesize{Simulated paths for Gompertz-lognormal process from $t_0=1$ to $t_{500}=100$, with values $m=1$, $\beta=0.2$, and $c=0.013$ and different values of noise; $\sigma^2=10^{-5}$, $\sigma^2=10^{-4}$, $\sigma^2=10^{-3}$ and  $\sigma^2=10^{-2}$. Black lines highlight the paths last value $x_{i;500}$ are maximum, minimum and the quartiles of the output range. }} \label{1:figura:path}
\end{figure}
